---
title: "p8105_hw1_jd3924.Rmd"
author: "Jiahe Deng"
date: "2022-09-24"
output: html_document
---
Question 1
```{r}
install.packages("palmerpenguins")
data("penguins", package = "palmerpenguins")
library(tidyverse)
penguins
```
```{r}
names(penguins)
nrow(penguins)
ncol(penguins)
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```
In the penguins, there are 8 catagories, which are"species","island", "bill_length_mm",bill_depth_mm","flipper_length_mm","body_mass_g", "sex" and "year". There are 344 entries with mean 200.9152. 
```{r}
ggplot(data=penguins,aes(flipper_length_mm, bill_length_mm,color= species)) +
  geom_point()
```
```{r}
ggsave(file = "flipper vs. bill.jpg")
```

Question 2
```{r,echo=TRUE}
my_df <- 
  tibble(
    my_sample <- rnorm(10),
    vac_logical <- my_sample > 0,
    vac_char <- c("a","b","c","d","e","f","g","h","i","j"),
    var_factor <- factor(c("bad","bad","welldone","bad","good","welldone",
                           "good","welldone","good","bad"))
)
my_df
mean(my_df$`my_sample <- rnorm(10)`)
mean(my_df$`vac_logical <- my_sample > 0`)
#only the vac_logical and my_sample are able to take the mean. 
#For my_sample, just take the sum and divided by n=10,then can get mean
#For vac_factor, any values that are greater than 0 counts as 1, and divided by n=10, then can get mean
#For vac_char and vac_favtor, they are strings, which are not able to get the mean
mean(pull(my_df,1))
mean(pull(my_df,2))
#convert logical, character, and factor variables to numeric
my_logical <- my_df$`vac_logical <- my_sample > 0`
logical_ <- as.numeric(my_logical)
my_factor <- my_df$`var_factor <- ...`
fac <- as.numeric(my_factor)
my_char <- my_df$`vac_char <- ...`
char <- as.numeric(my_char)
```
After applying the "as.numeric()"， we can see that only logic and factor can convert to numeric, character still not able to. For logical, since we divide out input into two categories, greater than or smaller than 0, so for input that greater than 0 has output TRUE counts are 1, and for input that smaller than 0 has output FALSE counts as 0. For factor, there are 3 different factor levels, which are welldone, good, and bad. So the computer can assign numbers 1 to 3 to bad, good and welldone accordingly. However, characters are still not able to convert to numeric because they are random characters that we made. To assign a number to each of the characters is not meaningful.
